\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-11 acl.2016/amta2016.tex
whatever

Also, stack pruning occurs on each hypothesis group independently, therefore, potentially affect search errors and model scores.

%Table~\ref{tab:stack-configuration} and 
Figure~\ref{fig:stack-configuration} present the tradeoff between decoding time and average model at various pop-limits. The model scores for all stack configurations are identical for low pop-limits but grouping hypotheses into coverage \& end position produces higher model scores for higher pop-limits. It is also slower but the time/quality tradeoff is better overall with this stack configuration. Model scores for coverage and cardinality configurations are identical, which differs from the results in ~\cite{ortizmartinez-garciavarea-casacuberta:2006:WMT}. This may be due to differing test set characteristics, or interactions with cube-pruning algorithm we used.
%\begin{table*}[t]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|r|r|r|r|} \hline
%Pop-limit	& \multicolumn{2}{c|}{Cardinality}	& \multicolumn{2}{c|}{Coverage}	& \multicolumn{2}{c|}{Coverage \& end pos} \\ \hline
%		& Time		& Score			& Time		& Score		& Time		& Score	\\ \hline
%100  		& 73		& -8.64513 		& 75		& -8.64513	& 72	& -8.64513 \\
%500		& 237		& -8.59563		& 225		& -8.59563 	& 229	& -8.59612 \\
%1,000	 	& 416		& -8.58700		& 397		& -8.58700	& 423	& -8.58700 \\ 
%5,000 		& 1930		& -8.58165		& 1931		& -8.58165	& 2153	& -8.58098 \\ 
%10,000 		& 3619		& -8.58133		& 3630		& -8.58133	& 4576	& -8.58015 \\ 
%15,000 		& 4830		& -8.58130		& 5001		& -8.58130	& 7156	& -8.57999 \\ 
%20,000 		& 5849		& -8.58130		& 5916		& -8.58130	& 9583	& -8.57994 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different stack configurations}
%\label{tab:stack-configuration}
%\end{table*}

@@

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
%

@@

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter. Using the tcmalloc library has a small positive effect on decoding speed but does little to improve scalability 
%\begin{figure}[h]
%\centering
%\begin{tabular}{cc}
%{\includegraphics[scale=0.5]{moses-scalability.png}} 
%\end{tabular}
%\caption{Moses' decoding speed}
%\label{fig:moses-speed}
%\end{figure}

@@

\subsection{Translation Quality}

Our work is intended as a drop-in replacement for the Moses decoder. Given the same parameters and models, the model scores are comparable and the search space should be identical (or very nearly identical). This should lead to almost identical translation quality, which we verify with Figure~\ref{fig:bleu}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality (BLEU) for different pop-limits}
\label{fig:bleu}
\end{figure}

>>>>

Also, stack pruning occurs on each hypothesis group independently, therefore, potentially affecting search errors and model scores.

%Table~\ref{tab:stack-configuration} and 
Figure~\ref{fig:stack-configuration} present the tradeoff between decoding time and average model, created by varying the cube-pruning pop-limit. The model scores for all stack configurations are identical for low pop-limits but grouping hypotheses into coverage \& end position produces higher model scores for higher pop-limits. It is also slower but the time/quality tradeoff is better overall with this stack configuration. Model scores for coverage and cardinality configurations are identical, which differs from the results in ~\cite{ortizmartinez-garciavarea-casacuberta:2006:WMT}. This may be due to differing test set characteristics, or interactions with cube-pruning algorithm we used.
%\begin{table*}[t]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|r|r|r|r|} \hline
%Pop-limit	& \multicolumn{2}{c|}{Cardinality}	& \multicolumn{2}{c|}{Coverage}	& \multicolumn{2}{c|}{Coverage \& end pos} \\ \hline
%		& Time		& Score			& Time		& Score		& Time		& Score	\\ \hline
%100  		& 73		& -8.64513 		& 75		& -8.64513	& 72	& -8.64513 \\
%500		& 237		& -8.59563		& 225		& -8.59563 	& 229	& -8.59612 \\
%1,000	 	& 416		& -8.58700		& 397		& -8.58700	& 423	& -8.58700 \\ 
%5,000 		& 1930		& -8.58165		& 1931		& -8.58165	& 2153	& -8.58098 \\ 
%10,000 		& 3619		& -8.58133		& 3630		& -8.58133	& 4576	& -8.58015 \\ 
%15,000 		& 4830		& -8.58130		& 5001		& -8.58130	& 7156	& -8.57999 \\ 
%20,000 		& 5849		& -8.58130		& 5916		& -8.58130	& 9583	& -8.57994 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different stack configurations}
%\label{tab:stack-configuration}
%\end{table*}

@@

%Also, the cube-pruning algorithm contain a priority queue per set of hypotheses sets. This can be independent of how hypotheses are grouped. In the Moses implementation, the priority queue is also attached to the coverage cardinality, Figure~\ref{algo:Cube Pruning with Unsorted Stack}.
%\begin{figure} [h]
%\begin{algorithmic}
%%\REQUIRE source sentence $s$, translation options
%\STATE initialize $queue_{|C|}$
%\FOR{1 to pop-limit}
%  \STATE get best $item$ in $queue_{|C|}$
%  \STATE create hypo from $item$, coverage $C_{new}$
%  \STATE add hypo to $stack_{|C_{new}|}$
%  \STATE create next $items$
%  \STATE add new $items$ to $queue_{|C|}$
%\ENDFOR % { hypothesis in $stack_i$} 
%\end{algorithmic}
%\caption{Cube Pruning with Cardinality Stacks}
%\label{algo:Cube Pruning with Unsorted Stack}
%\end{figure}
%Again, we experiment with diffirent queue configurations, having separate queues for each cardinality, coverage, and coverage \& end position. The stack configuration remained constant (coverage \& end position with pop-limit of 400).
%\begin{table}[h]
%\small
%\begin{center}
%\begin{tabular}{|r|r|r|} \hline
%Queue configuration		& Time		& Score \\ \hline
%Cardinality			& 192		& -8.59922 \\
%Coverage			& 2,413		& -8.58635 \\
%Coverage \& end position	& 7,472		& -8.58263 \\ \hline
%\end{tabular}
%\end{center}
%\caption{Decoding time (in secs with 32 threads) and average model scores for different queue configurations}
%\label{tab:queue-configuration}
%\end{table}
%From the results in Table~\ref{tab:queue-configuration}, using finer grain queues does results in better model scores but it is significantly slower to decode.
% 
We verified that the translation quality of our decoder is comparable to that of Moses in Figure~\ref{fig:bleu}. This fits in with our intention of creating a drop-in replacement for the Moses decoder. 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{bleu.png}} 
\end{tabular}
\caption{Translation quality (BLEU) for different pop-limits}
\label{fig:bleu}
\end{figure}

@@

This contrast with Moses where speed increases up to approximately 16 threads but then become slower thereafter. Using the tcmalloc library has a small positive effect on decoding speed but does little to improve scalability 
%\begin{figure}[h]
%\centering
%\begin{tabular}{cc}
%{\includegraphics[scale=0.5]{moses-scalability.png}} 
%\end{tabular}
%\caption{Moses' decoding speed}
%\label{fig:moses-speed}
%\end{figure}

@@
